Dependent Types and Martin-L\"of Type Theory: An Introduction

### 2016-07-04 paper.tex
yo

\section{Example Types and Sample Proofs}
Describe the section.

@@

ind𝔹 : (C : 𝔹 → Set) → C True → C False → (x : 𝔹) → C x
ind𝔹 C t f True = t
ind𝔹 C t f False = f
\end{code}
\end{minipage}
\end{center}

@@

\subsection*{Identity Types}
\begin{center}
\begin{minipage}{0.9\textwidth}
\begin{code}
infix  4  _≡_     -- propositional equality

data _≡_ {ℓ} {A : Set ℓ} : (a b : A) → Set ℓ where
  refl : (a : A) → (a ≡ a)

ind≡ : {A : Set} (C : {x y : A} → x ≡ y → Set) →
       (∀ (x : A) → C (refl x)) →
       {x y : A} (p : x ≡ y) → C p
ind≡ C c (refl x) = c x

rec≡ : {A : Set} {x y : A} (C : A → Set) → (p : x ≡ y) → C x → C y
rec≡ {A} {x} {y} C = 
  ind≡ (λ {x} {y} _ → C x → C y)
       (λ x → λ z → z)
       {x} {y} 
\end{code}
\end{minipage}
\end{center}

>>>>

\section{Example Types and Sample Proofs}
In this section, we present the type of Booleans, Natural numbers, Lists,
and the identity type. To further understand these types, we also include
a brief description of the different forms of equality, namely definitional,
judgmental and propositional. In type theory, the specific differences
between the three are generally misunderstood but are important in understanding
basic type theoretic proof methods, which we also go into some detail in
this section with several examples.

\subsection*{Equality}
%% talk about definitional equality, judgmental equality, prop equality

@@

ind𝔹 : (C : 𝔹 → Set) → C True → C False → (x : 𝔹) → C x
ind𝔹 C t f True = t
ind𝔹 C t f False = f
\end{code}
\end{minipage}
\end{center}
%% proof: 1 + 1 = 2

@@

\subsection*{Identity Types}
%% say something that this is the HoTT version of identity
%% possibly also point out that the discrepancy between the two
\begin{center}
\begin{minipage}{0.9\textwidth}
\begin{code}
infix  4  _≡_
data _≡_ {ℓ} {A : Set ℓ} : (a b : A) → Set ℓ where
  refl : (a : A) → (a ≡ a)

-- "PROPOSITIONAL EQUALITY"
-- For a proposition on an arbitrary identity type,
-- if we can show that it holds for (refl x), then
-- C holds for all proofs, p, such that x ≡ y.
J : {A : Set} (C : {x y : A} → x ≡ y → Set) →
    (∀ (x : A) → C (refl x)) →
    {x y : A} (p : x ≡ y) → C p
J C c (refl x) = c x

-- "STRICT EQUALITY"
-- For a proposition on a reflexive equality (x ≡ x),
-- if we can show that it holds for (refl x), then
-- C holds for all other reflexive equalities p : x ≡ x.
K : {A : Set} (C : {x : A} → x ≡ x → Set) →
    (∀ (x : A) → C (refl x)) →
    {x : A} (p : x ≡ x) → C p
K C c (refl x) = c x

rec≡ : {A : Set} {x y : A} (C : A → Set) →
       (p : x ≡ y) → C x → C y
rec≡ {A} {x} {y} C = 
  J (λ {x} {y} _ → C x → C y)
    (λ x → λ z → z)
    {x} {y} 
\end{code}
\end{minipage}
\end{center}
